working title Compatibility system and stigma size are the main predictors of heterospecific pollen effect

### 2019-03-06 Manuscript_draft/Manuscript_draft.Rmd
changes

pp1<- ggplot(some_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper,color=factor(Family)))+
  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")

@@

pp2<- ggplot(soly_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper,color=factor(Family)))+
  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")

@@

p3<- ggplot(sial_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper,color=factor(Family)))+
  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")

@@

p4<- ggplot(pein_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper,color=factor(Family)))+
  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")

@@

p5<- ggplot(ippu_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper,color=factor(Family)))+
  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")

@@

p6<- ggplot(ipaq_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper,color=factor(Family)))+
  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")

@@

p7<- ggplot(ersa_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper,color=factor(Family)))+
  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")

@@

p8<- ggplot(caan_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper,color=factor(Family)))+
  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")

@@

p9<- ggplot(brra_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper,color=factor(Family)))+
  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")

@@

p10<- ggplot(brol_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper,color=factor(Family)))+
  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")

>>>>

pp1<- ggplot(some_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper,color=factor(Family)))+
  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")

@@

pp2<- ggplot(soly_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper,color=factor(Family)))+
  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")

@@

p3<- ggplot(sial_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper,color=factor(Family)))+
  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")

@@

p4<- ggplot(pein_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper,color=factor(Family)))+
  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")

@@

p5<- ggplot(ippu_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper,color=factor(Family)))+
  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")

@@

p6<- ggplot(ipaq_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper,color=factor(Family)))+
  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")

@@

p7<- ggplot(ersa_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper,color=factor(Family)))+
  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")

@@

p8<- ggplot(caan_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper,color=factor(Family)))+
  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")

@@

p9<- ggplot(brra_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper,color=factor(Family)))+
  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("") + ylab("Hedges' g") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")

@@

p10<- ggplot(brol_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper,color=factor(Family)))+
  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("") + ylab("Hedges' g") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")
